\section{DATA}
\label{sec:data}

In this section we describe the data used for this analysis. We use data from the International Monetary Fund \href{https://www.imf.org/en/Data}{IMF} for the Gross Domestic Product (GDP) and the Interest Rates (IR) while the data about the Consumer Price Index was taken from the \href{https://www.worldbank.org/en/research/brief/inflation-database}{World Bank Group}. The data we were most interested in were the monthly values for our economics indicators to have a larger volume of data to use but we could only find quarterly data for the GDP. In order to have the same number of data points for all the indicators we decided to use linear interpolation to fill the missing values. The same procedure was similarly done for the Interest Rates as well but this only involved a few countries.

The data was then divided in three sections: training, test and COVID. The training data was used to train the models and contained all data up to the end of 2016. The test data was used to test the models and contained all data from the beginning of 2017 to the end of 2019. The COVID data was used to test the models in the presence of a situation outside the situation in which the models were trained and contained all data from the beginning of 2020 to the end of the available data. Moreover, the GDP data was expressed in hundred million dollars to have more manageable orders of magnitude.

After this preliminary analysis all countries that didn't have one of the indicators were removed. For data that either didn't have data for the test or COVID period, they were used differently depending on the model. For the initial correlation analysis we used all data available, for the Hidden Markov Model the data was used to train the model but it is not possible to test the model on the specific country. For the regression model, the countries that didn't have data for the test period where not considered viable for the analysis.

Overall, this leaves us with 25 countries for the correlation analysis and the Hidden Markov Model and 13 countries for the regression: Brazil, India, Indonesia, Italy, Israel, Mexico, Norway, Russia, South Africa, Switzerland, South Korea, Ukraine and United States.
